Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-11-18 Submission.Rmd
pushing to desktop - overwriting desktop (mostly attempts to format large cor table)

To provide descriptive context, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the top eight *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* (Figure \@ref(fig:combinegraphs2)) resources, challenges, and demands.[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide support for H1, and particularly so for hindrances.

@@

First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Job hindrances, however, exhibited relatively elevated associations across categories, with correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.

Regarding comparisons *across perception type*, the mean resource to challenge correlations within the same O\*Net grouping ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62). The correlations between resources and challenges *across* O\*Net grouping ranged from .08 to .50, *M* = .32, *SD* = .12 (for example, the correlation between mental processes [resource] and work output [challenge] was .39). The resource-hindrance correlations within the same O\*Net grouping ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* O\*Net grouping ranged from .05 to -.27 (*M* = -.14, *SD* = .08). The mean challenge to hindrance correlations within the same O\*Net grouping ranged from -.04 to -.27 (*M* = -.21, *SD* = .08). The correlations between challenges to hindrances across O\*Net grouping ranged from .12 to -.26, *M* = -.11, *SD* = .09.  In summary, observed correlations were larger  *within* O\*Net grouping than *across* (for all comparisons). Challenge and resource demands demonstrated the largest associations, with even the magnitude of across--category associations (.32) exceeding all hindrance perception associations -.11 to -.24). These results provide support for H2, -- particularly regarding what is perceived as a *resource* being also perceived as a *challenge*. Stated differently, job characteristics should not be uniquely categorized as resource or demand.

@@

Table 2 presents associations between total estimates of resource/ challenge/ hindrance within one's job and outcomes of engagement, stress, and burnout. Here, workers' perceptions were aggregated across all characteristics to provide "overall" resource and demand indices. Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate. The more percieved hindrances, the higher the rating of stress.

>>>>

For some descriptive context, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the top eight *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* (Figure \@ref(fig:combinegraphs2)) resources, challenges, and demands.[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide support for H1, and particularly so for hindrances.

@@

First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Job hindrances, however, exhibited relatively elevated associations across categories, with correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be more likely to be shared across different types of job activities, whereas challenges and resources can be relatively isolated within different job activities.

Regarding comparisons *across perception type*, the mean resource to challenge correlations within the same O\*Net grouping ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and information input challenges was .62). The correlations between resources and challenges *across* O\*Net grouping ranged from .08 to .50, *M* = .32, *SD* = .12 (for example, the correlation between mental processes [resource] and work output [challenge] was .39). The resource-hindrance correlations within the same O\*Net grouping ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* O\*Net grouping ranged from .05 to -.27 (*M* = -.14, *SD* = .08). The mean challenge to hindrance correlations within the same O\*Net grouping ranged from -.04 to -.27 (*M* = -.21, *SD* = .08). The correlations between challenges to hindrances across O\*Net grouping ranged from .12 to -.26, *M* = -.11, *SD* = .09.  In summary, observed correlations were larger  *within* O\*Net grouping than *across* (for all comparisons). Challenge and resource demands demonstrated the largest associations, with even the magnitude of across--category associations (.32) exceeding all hindrance perception associations -.11 to -.24). These results provide support for H2 -- particularly regarding *resource* and *challenge* perceptions. Stated differently, job characteristics should not be expected to be uniquely categorized as resource or demand.

@@

The consequences of demands and resources are theoretically varied. Table 2 presents empirical  associations between estimates of resource, challenge, and hindrance and worker *engagement*, *stress*, and *burnout*. Here, workers' perceptions were aggregated across all characteristics to provide indications of "overall" resource and demand experience. Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate. The more percieved hindrances, the higher the rating of stress.

### 2025-11-18 Submission.tex
pushing to desktop - overwriting desktop (mostly attempts to format large cor table)

H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource. Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items. Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances). These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).

To provide descriptive context, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the top eight \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} (Figure \ref{fig:combinegraphs2}) resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figure \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are limited to ``top eight'' characteristics per category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16). In sum, these results provide support for H1, and particularly so for hindrances.

>>>>

H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource. Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items. Here, the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances). These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).

For some descriptive context, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the top eight \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} (Figure \ref{fig:combinegraphs2}) resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figure \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are limited to ``top eight'' characteristics per category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16). In sum, these results provide support for H1, and particularly so for hindrances.
